---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# coperate

The goal of `coperate` is to facilitate the modelling of parametric copula-based models.
Resolving a copula model involves more than one step such as fitting a maximum likelihood model. It more often first requires choosing appropriate parametric copula families, their orientations, and sometimes even restricting the canonical parameter spaces. 

`coperate` cooperates with you to do this by

1. providing an extensive built-in selection of parametric copula models;
2. creating user-defined parametric copula families (optionally);
3. operating on the copula parameter space to restrict, relax, and alter the space; and
4. computing distributional quantities from a copula model,

This package intentionally does not include model-fitting functionality, such as MLE and CNQR, but is intended to be useful as a back-end for such fitting. 



## Installation

You can install coperate from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("vincenzocoia/coperate")
```


